Analysis

### 2022-07-30 production/prod_analysis-fix-t5.Rmd
ajustes plots y tablas

# Descriptive table __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) 
# extract variable labels
lab_study1 <- sjlabelled::get_label(df_study1) 
# convert items to factor
for (i in names(select(df_study1,starts_with("in_")))) {
  df_study1[[i]] <- factor(df_study1[[i]],1:5,get_labels(df_study1[[i]]))
}
# set variable labels
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
df_study1$in_amreal <- sjlabelled::set_label(df_study1$in_amreal,label = "Threat")

@@

@@

# Full sample_______________________________________________________________________
mat_full<- 
df_study_long_t5_comunas %>%
  # filter(ola==1) %>%
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_full <- as.matrix(mat_full$rho)
diag(cor_full) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_full) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_full) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Full sample")

# Wave 1_______________________________________________________________________
mat_1<- 
df_study_long_t5_comunas %>%
  filter(ola==1) %>%
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_1 <- as.matrix(mat_1$rho)
diag(cor_1) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_1) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_1) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_1,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 1")

# Wave 2_______________________________________________________________________
mat_2<-   
df_study_long_t5_comunas %>%
  filter(ola==2) %>% 
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_2 <- as.matrix(mat_2$rho)
diag(cor_2) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_2) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_2) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_2,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 2")

# Wave 3_______________________________________________________________________
mat_3 <- 
df_study_long_t5_comunas %>%
  filter(ola==3) %>% 
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_3 <- as.matrix(mat_3$rho)
diag(cor_3) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_3) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_3) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_3,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 3")

# Wave 4_______________________________________________________________________
mat_4 <- 
df_study_long_t5_comunas %>%
  filter(ola==4) %>% 
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_4 <- as.matrix(mat_4$rho)
diag(cor_4) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_4) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_4) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_4,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 4")

# Wave 5_______________________________________________________________________
mat_5 <- 
df_study_long_t5_comunas %>%
  filter(ola==5) %>% 
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_5 <- as.matrix(mat_5$rho)
diag(cor_5) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_5) <- c("A. Interaction anxiety with [PER/HAI/VEN]",
                     "B. Sympathy for [PER/HAI/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/HAI/VEN]",
                     "D. Friends value of immigrant friends [PER/HAI/VEN]",
                     "E. Immigrants [PER/HAI/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/HAI/VEN]",
                     "G. Loose of identity because of immigrants ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_5) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_5,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 5")
```

>>>>

# Descriptive table __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) 
# extract variable labels
lab_study1 <- sjlabelled::get_label(df_study1) 
# convert items to factor
for (i in names(select(df_study1,starts_with("in_")))) {
  df_study1[[i]] <- factor(df_study1[[i]],1:5,get_labels(df_study1[[i]]))
}
# set variable labels
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
df_study1$in_amreal <- sjlabelled::set_label(df_study1$in_amreal,label = "Threat (Unemployment increases)")

@@

```{r likert}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
# cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               sjlabelled,
               ggplot2,
               ggrepel,
               cowplot,
               sjPlot,
               ggpubr
)
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# Descriptive  __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm)

# para modelar estaba invertido:
#original: fraseo negativo: mayor acuerdo es "negativo" porque se pierde identidad
#recodificado: inversion de valores 5 es "menos perdida". Es positivo.
#ecodificado a sentido original para plot: 5 es "mayor perdida". Es negativo
sjmisc::frq(df_study1$in_amsimb)
sjmisc::frq(sjmisc::rec(df_study1$in_amsimb,rec = "rev"))
df_study1$in_amsimb <- sjmisc::rec(df_study1$in_amsimb,rec = "rev")
# extract variable labels
lab_study1 <- sjlabelled::get_label(df_study1)
# # convert items to factor
# for (i in names(select(df_study1,starts_with("in_")))) {
#   df_study1[[i]] <- factor(df_study1[[i]],1:5,get_labels(df_study1[[i]]))
# }
# set variable labels
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
df_study1$in_amreal <- sjlabelled::set_label(df_study1$in_amreal,label = "Threat (Unemployment increases)")
df_study1$in_amsimb <- sjlabelled::set_label(df_study1$in_amsimb,label = "Loose of identity because of migrants")

df_study1 <- 
  df_study1 %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         in_amreal)
# view_df(df_study1)

# se invierten todos los items para el plot, NO SU SENTIDO  para modelamiento
for (i in names(df_study1)) {
  df_study1[[i]] <- sjmisc::rec(x = df_study1[[i]],rec = "rev")  
}

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    # panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 18,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1
                                                                         )))
#

#Plot 1: Conviality-----------------------------------------------------------
p1<-
  dplyr::select(df_study1,in_ansied,in_simpat,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Conviviality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) +
  ggplot2::theme(legend.position = "none")

#Plot 2: Identity-------------------------------------------------------------
p2<-
  dplyr::select(df_study1,in_simili,in_amsimb,in_acpier,in_acadop) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Identity"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "none")

#Plot 3: Threat---------------------------------------------------------------
p3<-
  dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "none")

#Legend: Extract legend for the final plot using ggpubr
leg<- ggpubr::as_ggplot(
  ggpubr::get_legend(
    dplyr::select(df_study1,in_amreal) %>%
      sjPlot::plot_likert(geom.colors = "PuBu",
                          catcount = 4,
                          cat.neutral = 3) +
      ggplot2::theme(legend.position = "bottom") +
      ggplot2::scale_fill_manual(
        values = c("#b3b3b3ff", "#f1eef6ff", "#bdc9e1ff","#74a9cfff","#0570b0ff"),
        breaks=c("neutral",4,3,2,1),
        labels=c(
          "Neither comfortable nor uncomfortable\nSomewhat\nSomewhat similar\nNeither agree nor disagree\n",
          "Very uncomfortable\nVery little or not at all\nNot similar\nStrongly disagree",
          "Uncomfortable\nA little\nSlightly similar\nDisagree",
          "Comfortable\nQuite a lot\nQuite similar\nAgree",
          "Very comfortable\nA lot\nVery similar\nTotally agree")
      )
  )
)

# plot individuales-----------------------------------------------------------
colors<- c("#b3b3b3ff","#f1eef6ff","#bdc9e1ff","#74a9cfff","#0570b0ff")
p_ansied<-
  dplyr::select(df_study1,in_ansied) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Convivality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) + 
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither comfortable nor uncomfortable",      
      "Very uncomfortable",
      "Uncomfortable",
      "Comfortable",
      "Very comfortable"
    )
  )

p_simpat<-
  dplyr::select(df_study1,in_simpat) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Somewhat ",      
      "Very little or not at all",
      "A little",
      "Quite a lot",
      "A lot"
    )
  )

p_convi<-
  dplyr::select(df_study1,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: IDENTITY -----------------------------------------------
p_simili<-
  dplyr::select(df_study1,in_simili) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Identity"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Somewhat similar",      
      "Not similiar",
      "Slightly similar",
      "Quite similar",
      "Very similar"
    )
  )

p_identi<-
  dplyr::select(df_study1,in_amsimb,in_acpier,in_acadop,
                in_amsimb:in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: THREAT -----------------------------------------------
p_threat<-
    dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Disagree Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.35
m <- 0.6
l <- 0.7
#Final plot
likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 6, #4 plots
                       ncol = 1, #1 column
                       rel_heights = c(s,s,m,s,l,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "plot_likert2.png",
                plot = likert1,
                path = here::here("output/images"),
                device = "png",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)
pacman::p_load(cowplot)

#Final plot
likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(p_a,p_b,p_c,p_d, #plot 1,2,3 and legend (bottom)
                       align = "hv",
                       axis = "a",
                       nrow = 4, #4 plots
                       ncol = 1, #1 column
                       rel_heights = c(0.25,0.25,0.25,0.90) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align
  ) %>%
  cowplot::ggdraw()  
likert1
ggplot2::ggsave(filename = "plot_likert.png",
                plot = likert1,
                path = here::here("output/images"),
                device = "png",
                units = "cm",
                scale = 3,
                width = 10,height = 8)
```

@@

# Full sample_______________________________________________________________________
mat_full<- 
df_study_long_t5_comunas %>%
  # filter(ola==1) %>%
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

# dim(mat_full)

cor_full <- as.matrix(mat_full$rho)
diag(cor_full) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_full) <- c("A. Interaction anxiety with [PER/VEN]",
                     "B. Sympathy for [PER/VEN] living in Chile",
                     "C. Family value of migrant friends [PER/VEN]",
                     "D. Friends value of migrant friends [PER/VEN]",
                     "E. Migrants [PER/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/VEN]",
                     "G. Loose of identity because of migrants (reverse) ",
                     "H. Migrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_full) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Full sample")

png(file=here::here("output/images/plot_corr.png"),width=900, height=700)
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  # title = "\n Full sample"
  )
dev.off()

# Wave 1_______________________________________________________________________
mat_1<- 
df_study_long_t5_comunas %>%
  filter(ola==1) %>%
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>%   
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_1 <- as.matrix(mat_1$rho)
diag(cor_1) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_1) <- c("A. Interaction anxiety with [PER/VEN]",
                     "B. Sympathy for [PER/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/VEN]",
                     "D. Friends value of immigrant friends [PER/VEN]",
                     "E. Immigrants [PER/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/VEN]",
                     "G. Loose of identity because of immigrants (reverse) ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_1) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_1,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 1")

# Wave 2_______________________________________________________________________
mat_2<-   
df_study_long_t5_comunas %>%
  filter(ola==2) %>% 
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>%   
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_2 <- as.matrix(mat_2$rho)
diag(cor_2) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_2) <- c("A. Interaction anxiety with [PER/VEN]",
                     "B. Sympathy for [PER/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/VEN]",
                     "D. Friends value of immigrant friends [PER/VEN]",
                     "E. Immigrants [PER/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/VEN]",
                     "G. Loose of identity because of immigrants (reverse) ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_2) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_2,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 2")

# Wave 3_______________________________________________________________________
mat_3 <- 
df_study_long_t5_comunas %>%
  filter(ola==3) %>% 
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>%   
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_3 <- as.matrix(mat_3$rho)
diag(cor_3) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_3) <- c("A. Interaction anxiety with [PER/VEN]",
                     "B. Sympathy for [PER/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/VEN]",
                     "D. Friends value of immigrant friends [PER/VEN]",
                     "E. Immigrants [PER/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/VEN]",
                     "G. Loose of identity because of immigrants (reverse) ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_3) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_3,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 3")

# Wave 4_______________________________________________________________________
mat_4 <- 
df_study_long_t5_comunas %>%
  filter(ola==4) %>% 
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>%   
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()

cor_4 <- as.matrix(mat_4$rho)
diag(cor_4) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_4) <- c("A. Interaction anxiety with [PER/VEN]",
                     "B. Sympathy for [PER/VEN] living in Chile",
                     "C. Family value of immigrant friends [PER/VEN]",
                     "D. Friends value of immigrant friends [PER/VEN]",
                     "E. Immigrants [PER/VEN] have Chilean friends",
                     "F. Similarity between Chileans and [PER/VEN]",
                     "G. Loose of identity because of immigrants (reverse) ",
                     "H. Immigrant keeping their customs",
                     "I. Adoption of Chilean customs",
                     "J. Unemployment increases")
#set Column names of the matrix
colnames(cor_4) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)","(H)","(I)","(J)")
#Plot the matrix using corrplot
corrplot::corrplot(cor_4,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  title = "\n Wave 4")

# Wave 5_______________________________________________________________________
mat_5 <- 
df_study_long_t5_comunas %>%
  filter(ola==5) %>% 
    select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>%   
  select(in_ansied,in_simpat,in_valfam, in_valami,in_amigcl, # conviviality
         in_simili,in_amsimb,in_acpier, in_acadop, # identity
         in_amreal # threat
         ) %>% 
  psych::mixedCor()
